|

### 2021-05-22 appendix/appendix.Rmd
cleaning up

3.  All other coeffients were not significant.

@@

With all coefficients, among the results of the effect sizes on the Log of Expenditure Per Capita Regressions, we find that in regard to the estimation method, papers that use `PANEL` data or `RDD`
   designs have smaller effects than articles that employ `OLS` estimations.

```{r}
# 2. Having the log of lower house seats (`logN`) as the main independent variable increases the detected effect.
```

All other results are insignificant.

@@

1. More recent papers find smaller effect sizes than older studies.

@@

1. Recent papers find even smaller effect sizes than older studies.

@@

6. The institution design: whether the legislature in the analysis is unicameral, bicameral, or mixed.

@@

The results follow below, and show null effects for all variables, including the intercept.

@@

1. Coefficients from non-majoritarian systems are significantly smaller than those found in purely majoritarian systems.

2. Compared with `OLS`, `PANEL`, `IV` and `RDD` report significantly smaller coefficients.

3. Evidence from purely unicameral systems produces significantly larger effect sizes.

@@

```{r}
#1. For the dependent variable, models with Log of Per Capita Expenditure tend to report significantly smaller effects than models with Per Capita Expenditure.

#2. For the independent variable, models with Log of Lower House Size tend to report significantly larger effects than models with Upper House Size.

#3. Over time, the reported coefficients have been increasing in size.

#4. Compared with `OLS`, `PANEL` and `RDD` report significantly smaller coefficients.

#5. All other moderators are insignificant.
```

>>>>

3.  All other moderators were not significant.

@@

With all coefficients, results of the effect sizes on the Log of Expenditure Per Capita Regressions indicate that in regard to the estimation method, papers that use `PANEL` data or `RDD` designs have smaller effects than articles that employ `OLS` estimations. All other results are insignificant.

@@

1. Recent papers find smaller effect sizes than older studies.

@@

1. Papers from more recent years find smaller effect sizes than older studies.

@@

6. The institutional design: whether the legislature in the analysis is unicameral, bicameral, or mixed.

@@

The results follow below, and show null effects for all variables except for Unicameral institutional designs.

@@

1. Coefficients from non-majoritarian systems are significantly lower than those found in purely majoritarian systems.

2. Compared with papers that employ `OLS`, those that use `PANEL`, `IV` and `RDD` report significantly smaller coefficients.

3. Evidence from unicameral systems presents significantly larger effect sizes.

@@
